---
title: "Junyi20 Summary Stats"
author: "Vikraanth Sinha"
date: "2023-07-03"
output: pdf_document
---

```{r}
library("dplyr")
library(psych)
```


Data: InfoUser
Contents: Demographic and performance info about students
Number of rows: 73K

```{r}
info_user <- read.csv('Info_UserData.csv')
head(info_user)
```


```{r}
# summary statistics
describe(info_user)
```




```{r}
# scatter matrix
info_user_num <- select_if(info_user, is.numeric)
plot(info_user_num, pch=20, cex=1.5, col='steelblue')
```

Meeting notes:

Want to predict points based on other variables
- Ex: does gender/city/being self-taught have an impact on scores?

Share smaller portions of dataset in dropbox folder

Hints: is the hint mechanism correlated w/performance of students?


To do:
histogram for each variable
statistical comparison between variables (t-test)
look at time series data analysis tutorial


```{r}
# linear model
lm_user <- lm(points~has_teacher_cnt, data=info_user)
summary(lm_user)
```

```{r}
# scatter plot with best fit line
plot(x=info_user$has_teacher_cnt, y=info_user$points, xlab="has teacher", ylab="points")
abline(lm_user)
```

```{r}
# diagnostic plots
plot(lm_user)
```


Dataset: InfoContent
Contents: info about learning material
Number of rows: 1.3K

```{r}
info_content <- read.csv('/Users/vikraanthsinha/Documents/work stuff/Online education/Junyi20/archive/Info_Content.csv')
# remove content_pretty_name, contains unicode characters that cause problems
head(info_content[, !names(info_content) %in% c("content_pretty_name")])
```



```{r}
# label encode categorical variables
for(i in 3:6)
{
  factors <- factor(info_content[,i])
  info_content[,i] <- as.numeric(factors)
}
head(info_content[, !names(info_content) %in% c("content_pretty_name")])
```


```{r}
describe(info_content)
```


Data: Log Problem
Content: info about problems and users who answered them
Number of rows: 16.2M

```{r}
log_problem <- read.csv('/Users/vikraanthsinha/Documents/work stuff/Online education/Junyi20/archive/Log_Problem.csv')
head(log_problem)
```


```{r}
describe(log_problem)
```


```{r}
junyi_subset <- read.csv('junyiSubset.csv')
head(junyi_subset)
```


```{r}
hist(junyi_subset$total_sec_taken, xlab="total time taken (sec)", main="Distribution of time taken on questions", breaks=seq(0, max(junyi_subset$total_sec_taken), by=max(junyi_subset$total_sec_taken)/ceiling(log2(nrow(junyi_subset))+1)))
```



```{r}
hist(junyi_subset$total_attempt_cnt, xlab="total attempts count", main="Distribution of number of attempts per question", breaks=ceiling(log2(nrow(junyi_subset))+1))
```



```{r}
hist(junyi_subset$used_hint_cnt, xlab="total attempts count", main="Distribution of hints used per question", breaks=ceiling(log2(nrow(junyi_subset))+1))
```


